Reading Notes

### 2020-08-04 2pd.tex
quick note about nfas

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was tang1986<cite> used a bilyaer structure
Saricifti and Heeger 1992 <cite> discovered BHJ
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
A-D-A \cite{Yi2018} has some mention of the A-D-A moeity and why it is good <read further>
<how opvs work>
The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
<why morphology matters>
<segue into simulation>

>>>>

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was tang1986<cite> used a bilyaer structure
Saricifti and Heeger 1992 <cite> discovered BHJ
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

<how opvs work>
The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
<why morphology matters>
<segue into simulation>
